new_analses

### 2021-07-06 Frontiers/Frontiers.Rmd
tr

Cite fancy references [@Neuro2013]. As demonstrated in @Gene2012, citations can
also be automatically reference. Multiple references are separated by semicolons
[@Neuro2013; @Neurobot2013].

@@

The experiment was conducted under field conditions at five locations: Arlington, WI (Washington County), Clay Center, NE (Clay County), Grant, NE (Perkins County), Lincoln, NE (Lancaster County), and Macomb, IL (McDonough County)

>>>>

kgghkg

@@

The experiment was conducted under field conditions at five locations: Arlington (Washington County, Wisconsin), Clay Center (Clay County, Nebraska), Grant (Perkins County, Nebraska), Lincoln (Lancaster County, Nebraska), and Macomb (McDonough County, Illinois)

Palmer amaranth flowering was monitored every other day throughout the study. When a plant started flowering, it was identified as male or female. Plant height was measured from soil surface to the plant apical meristem. Then, aboveground plant biomass was harvest near soil surface and oven dried at 65 C until reaching constant weight before the weight of biomass (g plant<sup>-1</sup>) was recorded.

## Statistical analyses {-}

The statistical analyses were performed using R statistical software version 4.0.1.

The cumulative Palmer amaranth flowering estimation was determined using a asymetrical three parameter log logistic Weibull function of the drc package .

$$Y(x) = 0 + (d-0) exp (-exp(b(log(x)-e)))$$
In this model, *Y* is the Palmer amaranth cumulative flowering, *d* is the upper limit (set to 100), and *e* is the XXX, and *x* day of year.

### 2021-07-06 Frontiers/Frontiers.tex
tr

Cite fancy references (\textbf{Neuro2013?}). As demonstrated in
(\textbf{Gene2012?}), citations can also be automatically reference.
Multiple references are separated by semicolons (\textbf{Neuro2013?};
\textbf{Neurobot2013?}).

@@

\hypertarget{plant-material}{%
\subsection*{Plant material}\label{plant-material}}
\addcontentsline{toc}{subsection}{Plant material}

The study was performed with a \emph{A. palmeri} accession (Per1) from
Perkins County, Nebraska. Per1 accession collection is documented in
(Oliveira et al., 2021), with no reported herbicide resistance. Seeds
were planted in plastic trays containing potting-mix. Emerged seedlings
(1 cm) were transplated into 200 cm-3 plastic pots. Palmer amaranth
seedlings supplied with adequate water and kept under greenhouse
conditions at 28/20 C day/night temperature with 80\$ relative humidity.
Artificial lighting was provided using metal halide lamps (600 mmol m-2
s-1) to ensure 15-h photoperiod.

The experiment was conducted under field conditions at five locations:
Arlington, WI (Washington County), Clay Center, NE (Clay County), Grant,
NE (Perkins County), Lincoln, NE (Lancaster County), and Macomb, IL
(McDonough County)

>>>>

kgghkg

@@

\hypertarget{plant-material-and-growing-conditions}{%
\subsection*{Plant material and growing
conditions}\label{plant-material-and-growing-conditions}}
\addcontentsline{toc}{subsection}{Plant material and growing conditions}

The study was performed with a \emph{A. palmeri} accession (Per1) from
Perkins County, Nebraska. Per1 accession collection is documented in
(Oliveira et al., 2021), with no reported herbicide resistance. Seeds
were planted in plastic trays containing potting-mix. Emerged seedlings
(1 cm) were transplanted into 200 cm-3 plastic pots (a plant pot-1).
Palmer amaranth seedlings were supplied with adequate water and kept
under greenhouse conditions at Arlington, Clay Center, Lincoln, and
Macomb; and kept outdoors in Grant. At 7 to 10 cm height, Palmer
amaranth seedlings were transplanted to the field for the onset of the
experiment.

\hypertarget{field-study}{%
\subsection*{Field study}\label{field-study}}
\addcontentsline{toc}{subsection}{Field study}

The experiment was conducted under field conditions at five locations:
Arlington (Washington County, Wisconsin), Clay Center (Clay County,
Nebraska), Grant (Perkins County, Nebraska), Lincoln (Lancaster County,
Nebraska), and Macomb (McDonough County, Illinois)

Palmer amaranth flowering was monitored every other day throughout the
study. When a plant started flowering, it was identified as male or
female. Plant height was measured from soil surface to the plant apical
meristem. Then, aboveground plant biomass was harvest near soil surface
and oven dried at 65 C until reaching constant weight before the weight
of biomass (g plant-1) was recorded.

\hypertarget{statistical-analyses}{%
\subsection*{Statistical analyses}\label{statistical-analyses}}
\addcontentsline{toc}{subsection}{Statistical analyses}

The statistical analyses were performed using R statistical software
version 4.0.1.

The cumulative Palmer amaranth flowering estimation was determined using
a three parameter log logistic Weibull function of the drc package .

\[Y(x) = 0 + (d-0) exp (-exp(b(log(x)-e)))\] In this model, \emph{Y} is
the Palmer amaranth cumulative flowering, \emph{d} is the upper limit
(set to 100), and \emph{e} is the XXX, and \emph{x} day of year.

### 2021-07-06 new_analyses.Rmd
tr

ed_values1 %>% 
  filter(crop == "corn") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>% 
  ggplot(aes(x = location, y = estimate)) +
  scale_x_reordered() +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 153, ymax= 183), 
            fill = "#FFFDD0", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 153, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2, color = c("#8B8000", "#80461b", 
                                  "darkgreen", "blue")) +
  labs(y = NULL, x = NULL,
       title = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  geom_curve(data = rect1, aes(x = x, y = y, 
                               xend = xend, yend = yend),
             arrow = arrow(length = unit(0.07, "inch")), 
               size = 0.4, curvature = 0.3) + 
  geom_text(data = label1, 
            aes(x = x, y = y), 
            size = 2,
            label = label2$label, color = "red") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(),
        strip.text = element_markdown(face = "bold"),
        plot.title.position = "plot") -> p1c
```

@@

ed_values1 %>% 
  filter(crop == "fallow") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>% 
  ggplot(aes(x = location, y = estimate)) +
  scale_x_reordered() +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 153, ymax= 183), 
            fill = "#FFFDD0", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 153, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2, color = c("#8B8000", "#80461b", 
                                  "darkgreen", "blue")) +
  labs(y = "Day of year", x = NULL,
       title = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(),
        strip.text = element_markdown(face = "bold"),
        plot.title.position = "plot") -> p1f
```

@@

ed_values1 %>% 
  filter(crop == "corn") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>% 
  ggplot(aes(x = location, y = estimate)) +
  scale_x_reordered() +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 153, ymax= 183), 
            fill = "#FFFDD0", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 153, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2, color = c("#8B8000", "#80461b", 
                                  "darkgreen", "blue")) +
  labs(y = NULL, x = NULL,
       title = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(),
        strip.text = element_markdown(face = "bold"),
        plot.title.position = "plot") -> p1s
```

@@

```{r}
ed_values3 %>% 
  filter(crop == "corn") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>%
  ggplot(aes(x = location,
             y = estimate)) +
  scale_x_reordered() +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 183, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2.5, color = c("#80461b", "darkgreen", "blue")) +
  labs(y = NULL, x = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  geom_curve(data = rect2, aes(x = x, y = y, 
                               xend = xend, yend = yend),
             arrow = arrow(length = unit(0.07, "inch")), 
               size = 0.4, curvature = 0.3) + 
  geom_text(data = label2, 
            aes(x = x, y = y), 
            size = 2,
            label = label2$label, color = "red") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold"),
        plot.title = element_markdown(),
        plot.title.position = "plot") -> p2c
```

@@

```{r}
ed_values3 %>% 
  filter(crop == "fallow") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>%
  ggplot(aes(x = location,
             y = estimate)) +
  scale_x_reordered() +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 183, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2.5, color = c("#80461b", "darkgreen", "blue")) +
  labs(y = "Day of year", x = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold"),
        plot.title = element_markdown(),
        plot.title.position = "plot") -> p2f
```

@@

ed_values3 %>% 
  filter(crop == "soybean") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>%
  ggplot(aes(x = location,
             y = estimate)) +
  scale_x_reordered() +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 183, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2.5, color = c("#80461b", "darkgreen", "blue")) +
  labs(y = NULL, x = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold"),
        plot.title = element_markdown(),
        plot.title.position = "plot") -> p2s
p2s
```

>>>>

ed_values1 %>% 
  filter(crop == "corn") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>% 
  ggplot(aes(x = location, y = estimate)) +
  scale_x_reordered(expand = c(.01, .01)) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 153, ymax= 183), 
            fill = "#FFFDD0", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 153, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2, color = c("#8B8000", "#80461b", 
                                  "darkgreen", "blue")) +
  labs(y = NULL, x = NULL,
       title = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  geom_curve(data = rect1, aes(x = x, y = y, 
                               xend = xend, yend = yend),
             arrow = arrow(length = unit(0.07, "inch")), 
               size = 0.4, curvature = 0.3) + 
  geom_text(data = label1, 
            aes(x = x, y = y), 
            size = 2,
            label = label1$label, color = "red") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(),
        strip.text = element_markdown(face = "bold"),
        plot.title.position = "plot") -> p1c
```

@@

ed_values1 %>% 
  filter(crop == "fallow") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>% 
  ggplot(aes(x = location, y = estimate)) +
  scale_x_reordered(expand = c(.01, .01)) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 153, ymax= 183), 
            fill = "#FFFDD0", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 153, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2, color = c("#8B8000", "#80461b", 
                                  "darkgreen", "blue")) +
  labs(y = "Day of year", x = NULL,
       title = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(),
        strip.text = element_markdown(face = "bold"),
        plot.title.position = "plot") -> p1f
```

@@

ed_values1 %>% 
  filter(crop == "corn") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>% 
  ggplot(aes(x = location, y = estimate)) +
  scale_x_reordered(expand = c(.01, .01)) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 153, ymax= 183), 
            fill = "#FFFDD0", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 153, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2, color = c("#8B8000", "#80461b", 
                                  "darkgreen", "blue")) +
  labs(y = NULL, x = NULL,
       title = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        plot.title = element_markdown(),
        strip.text = element_markdown(face = "bold"),
        plot.title.position = "plot") -> p1s
```

@@

```{r}
ed_values3 %>% 
  filter(crop == "corn") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>%
  ggplot(aes(x = location,
             y = estimate)) +
  scale_x_reordered(expand = c(.01, .01)) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 183, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2.5, color = c("#80461b", "darkgreen", "blue")) +
  labs(y = NULL, x = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  geom_curve(data = rect2, aes(x = x, y = y, 
                               xend = xend, yend = yend),
             arrow = arrow(length = unit(0.07, "inch")), 
               size = 0.4, curvature = 0.3) + 
  geom_text(data = label2, 
            aes(x = x, y = y), 
            size = 2,
            label = label2$label, color = "red") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold"),
        plot.title = element_markdown(),
        plot.title.position = "plot") -> p2c
```

@@

```{r}
ed_values3 %>% 
  filter(crop == "fallow") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>%
  ggplot(aes(x = location,
             y = estimate)) +
    scale_x_reordered(expand = c(.01, .01)) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 183, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2.5, color = c("#80461b", "darkgreen", "blue")) +
  labs(y = "Day of year", x = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold"),
        plot.title = element_markdown(),
        plot.title.position = "plot") -> p2f
```

@@

ed_values3 %>% 
  filter(crop == "soybean") %>% 
  mutate(ed = case_when(
    ed == "10" ~ "10% flowering",
    ed == "50" ~ "50% flowering",
    ed == "90" ~ "90% flowering",
    TRUE ~ "ed")) %>% 
  group_by(crop,  ed) %>% 
  mutate(location = reorder_within(location, 
                                   by = estimate, 
                                   within = ed)) %>%
  ggplot(aes(x = location,
             y = estimate)) +
  scale_x_reordered(expand = c(.01, .01)) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 183, ymax= 214), 
            fill = "#80461b", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 214, ymax= 244), 
            fill = "lightgreen", alpha=0.05) +
  geom_rect(mapping=aes(xmin= 0.5, xmax= 4.5,
                        ymin= 244, ymax= 274), 
            fill = "blue", alpha=0.05) +
  geom_hline(yintercept = 183, size = 1.1, 
             color = "red",
             alpha = 1) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower, ymax = upper), size = 1.2) +
  geom_text(data = month, aes(x = x, y = y), label = month$label,
            size = 2.5, color = c("#80461b", "darkgreen", "blue")) +
  labs(y = NULL, x = NULL) +
  facet_grid(ed ~ crop, scales = "free_y") +
  coord_flip() +
  theme_test() +
  theme(legend.position = "none",
        strip.text = element_markdown(face = "bold"),
        plot.title = element_markdown(),
        plot.title.position = "plot") -> p2s
p2s
```
